Multilevel computation of glacier geometry \\ from Stokes dynamics

### 2021-05-28 paper/msg.tex
Minor reword.

If $\alpha=(F^h)'(s^h)[\psi_i,\psi_i]$ is positive then the solution of \eqref{eq:fepointwisevi} is
\begin{equation}
  c = \max\left\{-\frac{\rho_i(s^h; 0)}{\alpha}, \omega_i^{s^h}\right\}, \label{eq:fepointwisevisolution}
\end{equation}
which generalizes a well-known formula for the classical obstacle problem \cite[formula (4.4), for example]{GraeserKornhuber2009}.  However, if $\alpha\le 0$ then the model has degenerated in the sense that the linearized operator is not acting elliptically with respect to that perturbation.  In that case we make no change to $s^h$; we set $c=0$.  While one can prove in the shallow, flat-bed model that the analogous $\alpha$ alpha quantity is positive on the icy part of $\Omega$ \cite{JouvetBueler2012}, which follows since the equation is elliptic, the full Glen-Stokes model allows no such guarantee to our knowledge.

>>>>

If $\alpha=(F^h)'(s^h)[\psi_i,\psi_i]$ is positive then the solution of \eqref{eq:fepointwisevi} is
\begin{equation}
  c = \max\left\{-\frac{\rho_i(s^h; 0)}{\alpha}, \omega_i^{s^h}\right\}, \label{eq:fepointwisevisolution}
\end{equation}
which generalizes a well-known formula for the classical obstacle problem \cite[formula (4.4), for example]{GraeserKornhuber2009}.  However, if $\alpha\le 0$ then the model has degenerated in the sense that the linearized operator is not acting elliptically with respect to that perturbation.   In that case we make no change to $s^h$; we set $c=0$.  Because the interior PDE in the shallow, flat-bed model is elliptic, one can prove that the analogous $\alpha$ is positive on the icy part of $\Omega$ \cite{JouvetBueler2012}, but the full Glen-Stokes model here allows no such guarantee to our knowledge.
